---
title: 'Week2 Practice Problems'
author: "yamur"
date: "2022-07-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE}
library("ggplot2")
```

## Problem Set 1
### Review Sections 2.1-2.5 from Hands-On Programming in R and complete the following exercises: 
```{r roll}
roll <- function() {
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE)
  sum(dice)
}
```

```{r roll2}
roll2 <- function(bones=1:6) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
```

#### Test
```{r test}
roll2()
roll2(1:4)
```

### Review Sections 3.1 - 3.4 from Hands-On Programming in R and complete the following exercises

In a new code chunk in your Rmd file, produce a histogram of 50,000 rolls of three 8 sided fair dice. 

```{r roll3}
roll3 <- function(bones=1:8, size=2) {
  dice <- sample(bones, size = size, replace = TRUE)
  sum(dice)
}

roll3(bones = 1:8, size=3)
```

```{r qplot}
# qplot makes a histogram when you give it a single vector.
rolls3 <- replicate(10000, roll3())
qplot(rolls3, binwidth = 1)
```

Then do the same thing where the dice are loaded so that the number 7 has a higher probability of being rolled than the other numbers, assume all the other numbers have a 1/10 probability of being rolled.

```{r weighted dice}
roll4 <- function() {
  die <- 1:8
  dice <- sample(die, size = 3, replace = TRUE, 
    prob = c(1/10, 1/10, 1/10, 1/10, 1/10, 3/10,1/10,1/10))
  sum(dice)
}
```

```{r weighted dice qplot}
# qplot makes a histogram when you give it a single vector.
rolls4 <- replicate(10000, roll4())
qplot(rolls4, binwidth = 1)
```


### Finally

Rewrite the "rescale01()" function such that -Inf is mapped to 0 and Inf is mapped to 1.
```{r}
x <- c(1:10,-Inf, Inf)
rescale01 <- function(v){
  rng <- range(v, na.rm=FALSE,finite = TRUE)
  v <- (v-rng[1])/(rng[2]-rng[1])
  # -Inf is mapped to 0 and Inf is mapped to 1.
  ifelse(is.finite(v), v, ifelse(v > 0, 1, 0))
}
rescale01(x)
```

Write both_na(), a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors.

```{r NA}
x <- c(0, 1, NA, NA, NA, 3, -4, NA)
y <- c(-3, NA, 0, NA, NA, NA, 0, 1)

# one line solution (for loop would also do the job but not efficient)
both_na <- function(x, y){
  which(is.na(x) & is.na(y))
}

both_na(x,y)
```








