---
title: "Tidying Data Practice"
output: github_document
---

##### Libraries
Load the tidyverse library
```{r}
library(tidyverse)
```

##### Question 1. 
The following built-in datasets are not tidy. For each one, describe why it is not tidy, write out what the first five entries would look like once it is in a tidy format, and then tidy the dataset 

a.relig_income
b.billboard
c.us_rent_income

```{r}
# relig_income
# a row should only contain one observation

relig_income %>%
    pivot_longer(!religion, names_to = "income", values_to = "count")

# billboard
# a row should only contain one observation

billboard %>%
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    names_prefix = "wk",
    values_to = "rank",
    values_drop_na = TRUE
  )


# us_rent_income

us_rent_income %>%
  pivot_wider(
    names_from = variable,
    names_glue = "{variable}_{.value}",
    values_from = c(estimate, moe)
  )
```

##### Question 2.
2.Use "pivot_longer" to tidy the built-in table4b dataset

```{r question-2-response}
table4b %>% 
  pivot_longer(
    -country,
    names_to = "year",
    values_to = "population",
  )

```

##### Question 3. 
3.Import and tidy the monkeymen dataset. The cell values represent identification accuracy of some objects (in percent of 20 trials).

```{r question-3-response}
monkeymem <- read_csv(
  "monkeymem.csv", 
  col_types = cols(
    Monkey = col_character(),
    Treatment = col_factor(levels = c("Control","Treated"))
  )
)

monkeymem %>% 
  pivot_longer(
    cols = starts_with("Week"),
    names_to = "Week",
    names_prefix = "Week",
    values_to = "Accuracy",
  )
```

##### Question 4. 
4. As explained in the lecture video load and tidy the built in world_bank_pop data frame

```{r question-4-response}
world_bank_pop %>% 
  pivot_longer(
    cols = starts_with("20"),
    names_to = "Year",
    values_to = "Population",
  )
```

##### Question 5.
1.  In the following data set, turn the implicit missing values to explicit.

```{r}
output <- tibble(
      treatment   = c("a", "b", "a", "c", "b"),
      gender   = factor(c("M", "F", "F", "M", "M"), levels = c("M", "F", "O")),
      return = c(1.5, 0.75,  0.5,  1.8,  NA)
    )
output  %>%
  complete(treatment, gender)
```

##### Question 6.
Read the dataset available at "https://raw.githubusercontent.com/JaneWall/data_STAT412612/master/weather.csv" as weather. 

Use "pivot_longer()" to to put the days all in one column, then use "pivot_wider" to separate tmax and tmin into separate columns. Print the summary of the final resulting dataset.

```{r}
weather <- read_csv(url("https://raw.githubusercontent.com/JaneWall/data_STAT412612/master/weather.csv"))
weather %>% 
  pivot_longer(
    cols = starts_with("d"),
    names_to = "Day",
    values_to = "Temp",
  )  %>% 
  pivot_wider(
    names_from = element,
    values_from = c(Temp)
  )

```

##### Question 7.
Load the built in "anscombe" data frame and use "pivot_longer()" to separate all the x and y columns and categorize them into 4 sets.

```{r}
anscombe %>%
  pivot_longer(
    everything(),
    names_to = c(".value", "set"),
    names_pattern = "(.)(.)"
  )
```
