---
title: "Tidying Data Assignment"
output: github_document
---
# Please complete all the tasks listed below. After completing the tasks download the .Rmd file and upload in the peer review item for grading.

# Additionally please write text between the code chunks explaining what each code chunk is about.

# Refer the linked online textbook in case of any issues.

Load the tidyverse library
```{r}
library(tidyverse)
```

##### Question 1. 

The built in billboard dataset is not tidy. Describe why it is not tidy and then tidy the dataset.

```{r question-1-response}

# First gather up all the week entries into a row for each week for each song (where there is an entry)

billboard %>%
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    names_prefix = "wk",
    values_to = "rank",
    values_drop_na = TRUE
  )

# Then, convert the week variable to a number and figure out the date corresponding to each week on the chart

billboard %>%
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    names_prefix = "wk",
    values_to = "rank",
    values_drop_na = TRUE
  ) %>%
  mutate(date = date.entered + (as.integer(week) - 1) * 7)

# Sort the data by artist, track and week. Here are what your first entries should be (formatting can be different):
billboard %>%
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    names_prefix = "wk",
    values_to = "rank",
    values_drop_na = TRUE
  ) %>%
  mutate(date = date.entered + (as.integer(week) - 1) * 7) %>%
  arrange(artist, track, week)

#>  A tibble: 5,307 x 5
#   artist  track                   date.entered  week  rank   date
 #    <chr>   <chr>                   <date>       <int> <dbl>   <date>
 #  1 2 Pac   Baby Don't Cry (Keep... 2000-02-26       1    87 2000-02-26
 #  2 2 Pac   Baby Don't Cry (Keep... 2000-02-26       2    82 2000-03-04
 #  3 2 Pac   Baby Don't Cry (Keep... 2000-02-26       3    72 2000-03-11
 #  4 2 Pac   Baby Don't Cry (Keep... 2000-02-26       4    77 2000-03-18
 #  5 2 Pac   Baby Don't Cry (Keep... 2000-02-26       5    87 2000-03-25
 #  6 2 Pac   Baby Don't Cry (Keep... 2000-02-26       6    94 2000-04-01
 #  7 2 Pac   Baby Don't Cry (Keep... 2000-02-26       7    99 2000-04-08
 #  8 2Ge+her The Hardest Part Of ... 2000-09-02       1    91 2000-09-02
 #  9 2Ge+her The Hardest Part Of ... 2000-09-02       2    87 2000-09-09
 # 10 2Ge+her The Hardest Part Of ... 2000-09-02       3    92 2000-09-16
 # … with 5,297 more rows

```

##### Question 2. 

Tidy the "fish_encounters" dataset of fish spotting by monitoring stations. Make the NA into 0 using the option "values_fill = list(seen = 0)"


```{r question-2-response}
fish_encounters %>%
  complete(fish, station, fill = list(seen = 0))
```

##### Question 3. 

Import the flowers1 dataset. Tidy and pivot the data. Hint: use "read_csv2()" to read in the dataset 

```{r question-3-response}
flowers1 <- read_csv2("flowers1.csv")

flowers1 %>%
  pivot_wider(
    names_from = Variable,
    values_from = c(Value),
  )
```

##### Question 4.

Import the flowers2 dataset. Tidy the dataset by turning the one column into 3 separate columns

```{r question-4-response}
flowers2 <- read_csv2("flower2.csv")

flowers2 %>% 
  separate("Flowers/Intensity",c("Flowers", "Intensity"), "/")
```

##### Question 5.

In the following dataset, turn the implicit missing values to explicit 

```{r question-5-response}
output <- tibble(
      treatment   = c("a", "b", "a", "c", "b"),
      gender   = factor(c("M", "F", "F", "M", "M"), levels = c("M", "F", "O")),
      return = c(1.5, 0.75,  0.5,  1.8,  NA)
    )
output  %>%
  complete(treatment, gender)
```


#####Question 6.

Import the weather dataset as weather. Use "pivot_longer()" to put the days all in one column, then use "pivot_wider" to separate tmax and tmin into separate columns. Print the summary of the final resulting dataset 

```{r question-6-response}
weather <- read_csv(url("https://raw.githubusercontent.com/JaneWall/data_STAT412612/master/weather.csv"))
weather %>% 
  pivot_longer(
    cols = starts_with("d"),
    names_to = "Day",
    values_to = "Temp",
  )  %>% 
  pivot_wider(
    names_from = element,
    values_from = c(Temp)
  )
```

###### Question 7. 

Load the built in "anscombe" data frame and use "pivot_longer()" to separate all the x and y columns and categorize them into 4 sets

```{r question-7-response}
anscombe %>%
  pivot_longer(
    everything(),
    names_to = c(".value", "set"),
    names_pattern = "(.)(.)"
  )
```
