---
title: "My first Rmd"
author: "yamur"
date: "2022-07-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library_calls, message=FALSE, echo=FALSE}
library(tidyverse)
library(data.table)
library(rmarkdown)
```

## R Markdown

A bulleted list with sub-bullets under at least one item

* Item 1
* Item 2
    + *Item 2a*
    + **Item 2b**

A numbered list

1. Item 1
2. Item 2
3. Item 3
    + Item 3a
    + Item 3b

### Data

The results of some R code without showing the code

Cars
```{r cars, echo=FALSE}
summary(cars)
```

## Including Plots
A plot (show the code that generates the plot)
You can also embed plots, for example:
```{r pressure}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Table

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
Reference Style Links and Images


### My computer
```{r sessionInfo, message=FALSE}
sessionInfo()
```


