---
title: "Problem Set 4"
output: github_document
---

### Introduction

Reference the [tidyverse style guide](https://style.tidyverse.org/) while completing the exercises. 

These exercises are ungraded.

```{r lib, echo=FALSE}
library(tidyverse)
library(hflights)
library(nycflights13)
library(dplyr)
```

#### Question 1. 

Use the following definitions of cancellation codes to add a "Code" column to hflights, then use tail(hflights$Code[!is.na(hflights$Code)], n = 20) to see that your replacement worked by looking at the last 20 entries that are not NA. 

"A"   =    "carrier"
"B"  =    "weather"
"C"   =   "FF"
"D"   =   "security"
"E"   =   "not cancelled"

```{r}
lut <- c("A" = "carrier", "B"  =    "weather", "C"   =   "FF", "D"   =   "security", "E"   =   "not cancelled")
hflights$Code <- lut[hflights$CancellationCode]
tail(hflights$Code[!is.na(hflights$Code)], n = 20)
```

#### Question 2. 

What does the any_of() function do? Why might it be helpful in conjunction with this vector when analyzing nycflights13 data?

`vars <- c("year", "month", "day", "dep_delay", "arr_delay")`

any_of() is especially useful to remove variables from a data frame because calling it again does not cause an error:

#### Question 3. 

Does the result of running the following code surprise you? How does the select helpers deal with case by default? How can you change that default?

`select(flights, contains("TIME", ignore.case=FALSE))`

CASE INSENSIBLE, USE ignore.case=FALSE 

#### Question 4. 

Use select to show only the columns of hflights that have the word time or delay in the variable name or have the carrier id.

```{r}
select(flights, contains("TIME") | contains("DELAY") | contains ('CARRIER'))
```

#### Question 5. 

Find all flights from nycflights13 that had an arrival delay of two or more hours. Put the arrival delay first in your output so you can check it.

```{r}
flights %>%
  filter(arr_delay / 60 >= 2) %>%
  select(arr_delay, everything()) %>%
  arrange(desc(arr_delay))
```
#### Question 6. 

Find all flights from nycflights13 that were operated by United, American, or Delta.
```{r}
flights %>%
  filter(carrier %in% c('AA','UA','DL'))
```


#### Question 7.

Find all flights from nycflights13 that arrived more than two hours late.

```{r}
flights %>%
  filter(arr_delay / 60 >= 2) %>%
  select(arr_delay, everything()) %>%
  arrange(desc(arr_delay))
```

#### Question 8. 

Find all flights from nycflights13 that had a departure delay by at least an hour

```{r}
flights %>%
  filter(dep_delay / 60 >= 1) %>%
  select(dep_delay, everything()) %>%
  arrange(desc(dep_delay))
```

#### Question 9. 

Sort flights from nycflights13 to find the 5 most flights whose arrival was delayed the longest. Find the 5 flights that left earliest (most ahead of scheduled departure time). 

```{r}
flights %>%
  select(arr_delay, everything()) %>%
  arrange(desc(arr_delay)) %>%
  head(5)

flights %>%
  select(dep_delay, everything()) %>%
  arrange(dep_delay) %>%
  head(5)
```
